---
title: "My R Markdown Primer"
author: "Abidur Rahman"
date: "2026-04-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

R Markdown is a file format (.Rmd) and authoring framework for data science that lets users combine plain text, R code, and the results of that code in a single document. R Markdown documents allows users to create fully reproducible workflows and a wide array of static and dynamic output formats(e.g., HTML, PDF, and Word) that enables users to seamlessly document their analysis and share professional results with any audience.

## Narrative Section

One of the major benefits of using R Markdown is its ability to blend storytelling with computation. Instead of separating analysis and reporting, everything is knitted in one place. This improves transparency and reproducibility, since anyone can see both the code and the resulting output. It also reduces the chance of errors that often occur when copying results manually into a report.It also supports other languages, such as, Python, SQL, C++, etc, to be use in it's code chunks

## Mathematical Expressions
LaTeX Equations
Inline Equation: We can define the relationship between variables as $\alpha + \beta = \gamma$.
Display equation: 
$$\alpha + \beta = \gamma$$

## Code Chunk: Load Data

```{r}
# Load the built-in dataset mtcars
data(mtcars)

# Display the first few rows
head(mtcars)
```

## Code Chunk: Summary Statistics

```{r}
# Generate summary statistics of mtcars
summary(mtcars)
```

## Code Chunk: Visualization

```{r}
# Load ggplot2 for plotting
library(ggplot2)

# Create a scatter plot
ggplot(mtcars, aes(x = wt, y = mpg)) +
  geom_point(color = "blue") +
  labs(title = "Car Weight vs MPG",
       x = "Weight",
       y = "Miles per Gallon")
```

## Conclusion

Using R Markdown is more efficient than writing plain data analysis reports because it integrates analysis and documentation in one place. It eliminates the need to manually copy results and ensures that outputs are always consistent with the underlying code. The benefits in reproducibility and organization make it a makes it superior for data-driven work compared to writing plain text.
